Exploratory data analysis

### 2021-04-01 analysis/eda.Rmd
restore old observation counts

```{r eda-12 }
vi_data_plot <- vi_data %>%
  mutate(plot = factor(rep(
    c("Laukiz 1", "Laukiz 2", "Luiando", "Oiartzun"),
    c(479, 451, 300, 529)
  )))
```

@@

```{r eda-18 }
plots <- list("Laukiz 1", "Laukiz 2", "Luiando", "Oiartzun")
dist <- map(plots, ~ {
  coords <- coords_vi_nri_clean %>%
    mutate(plot = factor(rep(
      c("Laukiz 1", "Laukiz 2", "Luiando", "Oiartzun"),
      c(479, 451, 300, 529)
    ))) %>%
    filter(plot == .x) %>%
    dplyr::select(-plot)
  points <- SpatialPoints(
    coords = coords,
    # EPSG: 25830
    proj4string = CRS("+proj=utm +zone=30 +ellps=WGS84 +datum=WGS84 +units=m +no_defs")
  )
  distance <- mean(as.dist(pointDistance(points,
    allpairs = TRUE,
    lonlat = FALSE
  )))
})
set_names(dist, plots)
dist_plots <- unlist(dist)
```

>>>>

```{r eda-12 }
vi_data_plot <- vi_data %>%
  mutate(plot = factor(rep(
    c("Laukiz 1", "Laukiz 2", "Luiando", "Oiartzun"),
    c(559, 451, 301, 497)
  )))
```

@@

```{r eda-18 }
plots <- list("Laukiz 1", "Laukiz 2", "Luiando", "Oiartzun")
dist <- map(plots, ~ {
  coords <- coords_vi_nri_clean %>%
    mutate(plot = factor(rep(
      c("Laukiz 1", "Laukiz 2", "Luiando", "Oiartzun"),
      c(559, 451, 301, 497)
    ))) %>%
    filter(plot == .x) %>%
    dplyr::select(-plot)
  points <- SpatialPoints(
    coords = coords,
    # EPSG: 25830
    proj4string = CRS("+proj=utm +zone=30 +ellps=WGS84 +datum=WGS84 +units=m +no_defs")
  )
  distance <- mean(as.dist(pointDistance(points,
    allpairs = TRUE,
    lonlat = FALSE
  )))
})
set_names(dist, plots)
dist_plots <- unlist(dist)
```
